---
title: "Mini Data Analysis Milestone 2"
output: html_document
---

*To complete this milestone, you can either edit [this `.rmd` file](https://raw.githubusercontent.com/UBC-STAT/stat545.stat.ubc.ca/master/content/mini-project/mini-project-2.Rmd) directly. Fill in the sections that are commented out with `<!--- start your work here--->`. When you are done, make sure to knit to an `.md` file by changing the output in the YAML header to `github_document`, before submitting a tagged release on canvas.*

# Welcome to the rest of your mini data analysis project!

In Milestone 1, you explored your data. and came up with research questions. This time, we will finish up our mini data analysis and obtain results for your data by:

-   Making summary tables and graphs
-   Manipulating special data types in R: factors and/or dates and times.
-   Fitting a model object to your data, and extract a result.
-   Reading and writing data as separate files.

We will also explore more in depth the concept of *tidy data.*

**NOTE**: The main purpose of the mini data analysis is to integrate what you learn in class in an analysis. Although each milestone provides a framework for you to conduct your analysis, it's possible that you might find the instructions too rigid for your data set. If this is the case, you may deviate from the instructions -- just make sure you're demonstrating a wide range of tools and techniques taught in this class.

# Instructions

**To complete this milestone**, edit [this very `.Rmd` file](https://raw.githubusercontent.com/UBC-STAT/stat545.stat.ubc.ca/master/content/mini-project/mini-project-2.Rmd) directly. Fill in the sections that are tagged with `<!--- start your work here--->`.

**To submit this milestone**, make sure to knit this `.Rmd` file to an `.md` file by changing the YAML output settings from `output: html_document` to `output: github_document`. Commit and push all of your work to your mini-analysis GitHub repository, and tag a release on GitHub. Then, submit a link to your tagged release on canvas.

**Points**: This milestone is worth 50 points: 45 for your analysis, and 5 for overall reproducibility, cleanliness, and coherence of the Github submission.

**Research Questions**: In Milestone 1, you chose two research questions to focus on. Wherever realistic, your work in this milestone should relate to these research questions whenever we ask for justification behind your work. In the case that some tasks in this milestone don't align well with one of your research questions, feel free to discuss your results in the context of a different research question.

# Learning Objectives

By the end of this milestone, you should:

-   Understand what *tidy* data is, and how to create it using `tidyr`.
-   Generate a reproducible and clear report using R Markdown.
-   Manipulating special data types in R: factors and/or dates and times.
-   Fitting a model object to your data, and extract a result.
-   Reading and writing data as separate files.

# Setup

Begin by loading your data and the tidyverse package below:

```{r, message = FALSE}
library(datateachr) # <- might contain the data you picked!
library(tidyverse)
```

# Task 1: Process and summarize your data

From milestone 1, you should have an idea of the basic structure of your dataset (e.g. number of rows and columns, class types, etc.). Here, we will start investigating your data more in-depth using various data manipulation functions.

### 1.1 (1 point)

First, write out the 4 research questions you defined in milestone 1 were. This will guide your work through milestone 2:

<!-------------------------- Start your work below ---------------------------->

1.  Are there specific regions within the city that have distinct patterns of time limits, and how do these patterns affect parking rates? I would like to explore the distribution of parking rates and time limits in different areas within the city.

2.  Do areas with shorter time limits tend to have lower parking rates, and vice versa? I would like to explore the relationship between parking rates and time limits.

3.  Does the acceptance of credit card relate to parking rates? I would like to explore whether the payment method will affect the rates.

4.  How do the geographical coordinates (latitude and longitude) of parking spaces influence pricing and time limits? In addition to analyzing regional patterns, I also plan to plot precise maps of parking space coordinates, allowing us to visualize their distribution and its relation to pricing and time limits.

    <!----------------------------------------------------------------------------->

Here, we will investigate your data using various data manipulation and graphing functions.

### 1.2 (8 points)

Now, for each of your four research questions, choose one task from options 1-4 (summarizing), and one other task from 4-8 (graphing). You should have 2 tasks done for each research question (8 total). Make sure it makes sense to do them! (e.g. don't use a numerical variables for a task that needs a categorical variable.). Comment on why each task helps (or doesn't!) answer the corresponding research question.

Ensure that the output of each operation is printed!

Also make sure that you're using dplyr and ggplot2 rather than base R. Outside of this project, you may find that you prefer using base R functions for certain tasks, and that's just fine! But part of this project is for you to practice the tools we learned in class, which is dplyr and ggplot2.

**Summarizing:**

1.  Compute the *range*, *mean*, and *two other summary statistics* of **one numerical variable** across the groups of **one categorical variable** from your data.
2.  Compute the number of observations for at least one of your categorical variables. Do not use the function `table()`!
3.  Create a categorical variable with 3 or more groups from an existing numerical variable. You can use this new variable in the other tasks! *An example: age in years into "child, teen, adult, senior".*
4.  Compute the proportion and counts in each category of one categorical variable across the groups of another categorical variable from your data. Do not use the function `table()`!

**Graphing:**

6.  Create a graph of your choosing, make one of the axes logarithmic, and format the axes labels so that they are "pretty" or easier to read.
7.  Make a graph where it makes sense to customize the alpha transparency.

Using variables and/or tables you made in one of the "Summarizing" tasks:

8.  Create a graph that has at least two geom layers.
9.  Create 3 histograms, with each histogram having different sized bins. Pick the "best" one and explain why it is the best.

Make sure it's clear what research question you are doing each operation for!

<!------------------------- Start your work below ----------------------------->

Before doing any work, I first made a subset from the original 'parking_meter' dataset that only focuses on the specific research questions. I converted \<chr\> numerical values to \<dbl\>, i.e. '\$1.00' to 1, '2 Hr' to 2. I also replaced 'No Time Limit' with 24 in the time limit variables since it means everyone can park there forever but it is impractical to put inf values for further analysis. I noticed the maximum time limit happens to be 26 hours in the original dataset, which is impossible. To address this problem, I replaced those values with NA. The new subset is denoted as 'm2', and is used throughout this milestone.

```{r}
m2 <- select(parking_meters, -c(meter_head,rate_misc,time_in_effect,time_misc,pay_phone,meter_id)) %>%

mutate(across(starts_with('r'), ~as.numeric(gsub('\\$', '', .)))) %>%

mutate(across(starts_with('t'), ~gsub('No Time Limit', '24 Hrs', .))) %>%

mutate(across(starts_with('t'), ~as.numeric(gsub('Hr|Hrs', '', .)))) %>%

mutate(across(starts_with('t'), ~as.numeric(gsub('26', NA, .)))) %>%
  
drop_na()

glimpse(m2)
```

Research Q1: Are there specific regions within the city that have distinct patterns of time limits, and how do these patterns affect parking rates? I would like to explore the distribution of parking rates and time limits in different areas within the city.

```{r}
# Option 1: Compute the range, mean, and two other summary statistics of one numerical variable across the groups of one categorical variable from your data.

q1_opt1 <- m2 %>%
  group_by(geo_local_area) %>%
  summarise('range ($)' = paste0(range(r_sa_9a_6p), collapse = '-'), 'mean ($)' = mean(r_sa_9a_6p),
            'median ($)' = median(r_sa_9a_6p), 'standard deviation ($)' = sd(r_sa_9a_6p))
glimpse(q1_opt1)
```

```{r}
# Option 6: Make a graph where it makes sense to customize the alpha transparency.
c <- group_by(m2,geo_local_area) %>%
  count(r_sa_9a_6p,t_sa_9a_6p)


q1_opt6 <- ggplot(c, aes(x = r_sa_9a_6p, y = geo_local_area)) +
  geom_jitter(colour = 'blue', aes(alpha = n, size = t_sa_9a_6p)) +
  scale_size_continuous(range = c(1.5,4)) +
  labs(
    title = 'Distribution of parking rates and time limits in different areas\nduring Saturday 6am - 9pm',
    x = 'Rate ($)',
    y = 'Area',
    size = 'Time limit (Hours)',
    alpha = 'Count'
  ) +
  theme(plot.title = element_text(size = 10))
plot(q1_opt6)
```

For Research Q1, Option 1 and 6 were selected. Opt.1 shows the range, mean, median, and standard deviation of the numerical variable r_sa_9a_6p (rate during Saturday 9am to 6pm) across the categorical variable geo_local_area, which gives me an impression of the characteristics of the numerical values in this dataset. Opt.6 shows the distribution of parking rates and time limits in different areas during Saturday 6am - 9pm. The customized alpha indicates the number of a specific parking rate and time limit. It can be concluded from the plot, for example, Downtown has more short-time but high-rate parking meters (small circle at high rates) and it doesn't have many long-time parking meters(big circle with low alpha).

---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------

Research Q2: Do areas with shorter time limits tend to have lower parking rates, and vice versa? I would like to explore the relationship between parking rates and time limits.

```{r}
# Option 3: Create a categorical variable with 3 or more groups from an existing numerical variable. You can use this new variable in the other tasks! An example: age in years into "child, teen, adult, senior".

q2_opt3.1 <- m2 %>%
  rowwise() %>%
  mutate(avg_rate = mean(c_across(starts_with("r")))) %>%
  mutate(avg_time = mean(c_across(starts_with("t")))) 
glimpse(q2_opt3.1)
```

```{r} # find the range to specify levels}
range(q2_opt3.1$avg_rate)
range(q2_opt3.1$avg_time)
```

```{r}
q2_opt3.2 <- q2_opt3.1 %>%
  mutate(rate_level = factor(case_when(avg_rate < 2 ~ "very low",
                                 avg_rate < 4 ~ "low",
                                 avg_rate < 6 ~ "moderate",
                                 avg_rate < 8 ~ "high",
                                  TRUE ~ "very high"),
                             levels = c('very low', 'low', 'moderate', 'high', 'very high'))) %>%
  
  mutate(time_level = factor(case_when(avg_time < 4 ~ "very low",
                                 avg_time < 8 ~ "low",
                                 avg_time < 12 ~ "moderate",
                                 avg_time < 16 ~ "high",
                                  TRUE ~ "very high"),
                             levels = c('very low', 'low', 'moderate', 'high', 'very high')))
glimpse(q2_opt3.2)
```

```{r}
# Option 8: Create a graph that has at least two geom layers.
q2_opt8 <- ggplot(q2_opt3.2) + geom_boxplot(aes(x = time_level, y = avg_rate)) + 
  geom_violin(aes(x = time_level, y = avg_rate), color = 'blue',alpha = 0.3) +
  labs(
    title = 'Average rate vs time limit levels',
    x = 'Time Limit Levels',
    y = 'Avg. Rate ($)',
  )
plot(q2_opt8)
```

For Research Q2, Option 3 and 8 were selected. Opt. 3 takes the average of parking rates and time limits for every row, which means it excluded the differences in time intervals. After that, I found the range of the averages and set the levels as very low, low, moderate, high, and very high. Then mutate the new variables to the dataset. Opt.8 shows a boxplot and a violin plot of average rate vs time limit levels. It clearly indicates that as time limit increases, the rate decreases, but there are some exceptions.

---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------

Research Q3: Does the acceptance of credit card relate to parking rates? I would like to explore whether the payment method will affect the rates.

```{r}
# Option 2: Compute the number of observations for at least one of your categorical variables. Do not use the function table()!

q3_opt2 <- q2_opt3.2 %>%
  group_by(geo_local_area,avg_rate) %>%
  count(credit_card)
glimpse(q3_opt2)
```

```{r}
# Option 8: Create a graph that has at least two geom layers.
q3_opt8 <- q3_opt2 %>%
ggplot() + 
  geom_boxplot(aes(x = credit_card, y = avg_rate)) + geom_jitter(aes(x = credit_card, y = avg_rate, color = geo_local_area), shape = 8) + 
  labs(
    title = 'Average rate vs acceptance of credit card in local areas',
    x = 'Acceptance of Credit Card',
    y = 'Avg. Rate ($)'
  ) + 
  theme(legend.title = element_text(size = 0))
plot(q3_opt8)
```

For Research Q3, Option 2 and 8 were selected. Opt. 2 counts the observations of credit card acceptance at each rate in each area. For example, an average rate of \$0.5 and cannot be paid with credit card in Downtown appears 6 time. This table is plotted in Opt.8, which is a combination of boxplot and jitterplot. It is obvious that parking meters that can be paid by credit cards have a higher average rate. Also, most of the parking meters do not accept credit card. Moreover, the majority of credit card paid areas appears to have a warmer color, e.g. Downtown, Fairview, West End.

---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------

Research Q4: How do the geographical coordinates (latitude and longitude) of parking spaces influence pricing and time limits? In addition to analyzing regional patterns, I also plan to plot precise maps of parking space coordinates, allowing us to visualize their distribution and its relation to pricing and time limits.

```{r}
#Option 2: Compute the number of observations for at least one of your categorical variables. Do not use the function table()!
q4_opt2 <- m2 %>%
  count(geo_local_area)
q4_opt2 
```

```{r}
# Option 8: Create a graph that has at least two geom layers.
canada <- map_data("world", region = "Canada")
ggplot(q2_opt3.1, aes(x = longitude, y = latitude)) + geom_polygon(data = canada, aes(x=long, y = lat, group = group),fill = 'white', color = 'black') + 
  coord_cartesian(xlim = c(-123.25, -123), ylim = c(49.21, 49.3)) + geom_point(size = 0.1)
```

```{r}

img <- jpeg::readJPEG('map.png')

# Plot with background image
ggplot(m2, aes(longitude, latitude))+
annotation_raster(img,
                    xmin = -Inf, xmax = Inf,
                    ymin = -Inf, ymax = Inf)
 #fill_palette("jco")
```

For Research Q4, Option 2 and 8 were selected. Opt. 2 counts the observations of credit card acceptance at each rate in each area. For example, an average rate of \$0.5 and cannot be paid with credit card in Downtown appears 6 time. This table is plotted in Opt.8, which is a combination of boxplot and jitterplot. It is obvious that parking meters that can be paid by credit cards have a higher average rate. Also, most of the parking meters do not accept credit card. Moreover, the majority of credit card paid areas appears to have a warmer color, e.g. Downtown, Fairview, West End.

---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------

<!----------------------------------------------------------------------------->

### 1.3 (2 points)

Based on the operations that you've completed, how much closer are you to answering your research questions? Think about what aspects of your research questions remain unclear. Can your research questions be refined, now that you've investigated your data a bit more? Which research questions are yielding interesting results?

<!------------------------- Write your answer here ---------------------------->

Q1. The question is nearly answered. From the plot I can see the distribution of the parking rates and time limits in different areas within the city. Most highly rated parking meters are located in Downtown. Most parking meters are located in Downtown, Kitsilano, and West End. Most parking rates are below \$2.5. The amount of high time limit with low rate are small. More detailed conclusions can be conducted in further analysis.

Q2. The question is nearly answered. From the plot I can see the relationship between parking rates and time limits. It clearly indicates that as time limit increases, the rate decreases. However, there are still some exceptions.

Q3. The question is nearly answered. From the plot I can see the relationship between payment method and parking rates. Parking meters that can be paid by credit cards have a higher average rate. Also, most of the parking meters do not accept credit card.

Q4. I tried to use a real world map as the background of the plot, but I couldn't figure it out. This assignment is limited to using ggplot so many other methods cannot be used. I've tried geom_sf(), geom_ploygon(), geom_map(), even imported jpeg package, which none of them worked. I guess the best way is to use a google map API or something else.

<!----------------------------------------------------------------------------->

# Task 2: Tidy your data

In this task, we will do several exercises to reshape our data. The goal here is to understand how to do this reshaping with the `tidyr` package.

A reminder of the definition of *tidy* data:

-   Each row is an **observation**
-   Each column is a **variable**
-   Each cell is a **value**

### 2.1 (2 points)

Based on the definition above, can you identify if your data is tidy or untidy? Go through all your columns, or if you have \>8 variables, just pick 8, and explain whether the data is untidy or tidy.

<!--------------------------- Start your work below --------------------------->

The dataset I used above is m2, which is currently tidy. Although there are 16 columns, every cell has its unique value. There were some NA values and outliers but I have addressed them at the beginning. If not limited to this question, I will calculate the average values for all rates and time limits for every time intervals. The resulting dataset should include only the average rate, average time limit, credit card information, coordinates, and geographic area data.

<!----------------------------------------------------------------------------->

### 2.2 (4 points)

Now, if your data is tidy, untidy it! Then, tidy it back to it's original state.

If your data is untidy, then tidy it! Then, untidy it back to it's original state.

Be sure to explain your reasoning for this task. Show us the "before" and "after".

<!--------------------------- Start your work below --------------------------->

Before (tidy):

```{r}
glimpse(m2)
```

After (untidy):

```{r}
untidy_m2 <- m2 %>%
  group_by(geo_local_area)%>%
  mutate(row = row_number()) %>%
# pivot longer rate
pivot_longer(
    cols = c(r_mf_9a_6p, r_mf_6p_10, r_sa_9a_6p, r_sa_6p_10, r_su_9a_6p, r_su_6p_10),
    names_to = "time_rate",
    values_to  ="rate") %>%
# pivot longer time
pivot_longer(
    cols = c(t_mf_9a_6p, t_mf_6p_10, t_sa_9a_6p, t_sa_6p_10, t_su_9a_6p, t_su_6p_10),
    names_to = "time_limit",
    values_to  ="limit") 
glimpse(untidy_m2)
```

After (tidy back):

```{r}
tidy_m2 <- untidy_m2 %>%

pivot_wider(
    names_from = time_rate,
    values_from = rate) %>%
pivot_wider(
    names_from = time_limit,
    values_from = limit) %>%
  
# reorder the variables
  
select(c(r_mf_9a_6p, r_mf_6p_10, r_sa_9a_6p, r_sa_6p_10, r_su_9a_6p, r_su_6p_10,t_mf_9a_6p, t_mf_6p_10, t_sa_9a_6p, t_sa_6p_10, t_su_9a_6p, t_su_6p_10,credit_card,longitude,latitude,geo_local_area))

glimpse(tidy_m2)
```

The original dataset is tidy. As instructed, I untidy it and re-tidy it. Now I create a new dataset that only includes the average rate, average time limit, credit card information, coordinates, and geographic area data.

```{r}
m2.1 <- m2 %>%
  rowwise() %>%
  mutate(avg_rate = mean(c_across(starts_with("r")), na.rm = TRUE)) %>%
  mutate(avg_time = mean(c_across(starts_with("t")), na.rm = TRUE)) %>%
  select(c(avg_rate,avg_time,credit_card,geo_local_area))
glimpse(m2.1)
```

<!----------------------------------------------------------------------------->

### 2.3 (4 points)

Now, you should be more familiar with your data, and also have made progress in answering your research questions. Based on your interest, and your analyses, pick 2 of the 4 research questions to continue your analysis in the remaining tasks:

<!-------------------------- Start your work below ---------------------------->

1.  Are there specific regions within the city that have distinct patterns of time limits, and how do these patterns affect parking rates? Do areas with shorter time limits tend to have lower parking rates, and vice versa? I would like to explore the distribution and relationship of parking rates and time limits in different areas within the city.
2.  Does the acceptance of credit card relate to parking rates? I would like to explore whether the payment method will affect the rates.

<!----------------------------------------------------------------------------->

Explain your decision for choosing the above two research questions.

<!--------------------------- Start your work below --------------------------->

I've decided to merge Q1 and Q2 since they are closely related and have the potential for conducting various intriguing analyses. I've also selected Q3 because it involves another categorical variable and has the potential to generate practical solutions. For instance, the parking company could consider implementing more credit card payment system to benefit more.

<!----------------------------------------------------------------------------->

Now, try to choose a version of your data that you think will be appropriate to answer these 2 questions. Use between 4 and 8 functions that we've covered so far (i.e. by filtering, cleaning, tidy'ing, dropping irrelevant columns, etc.).

(If it makes more sense, then you can make/pick two versions of your data, one for each research question.)

<!--------------------------- Start your work below --------------------------->

I modified the dataset from Task 1, q2_opt3.2. The new dataset, m2.2, will only include the avg_rate, avg_time, rate_level, time_level, credit_card, and geo_local_area variables.

```{r}
m2.2 <- q2_opt3.2 %>%
  select(c(avg_rate,avg_time,rate_level, time_level, credit_card,geo_local_area))
glimpse(m2.2)
```

# Task 3: Modelling

## 3.0 (no points)

Pick a research question from 1.2, and pick a variable of interest (we'll call it "Y") that's relevant to the research question. Indicate these.

<!-------------------------- Start your work below ---------------------------->

**Research Question**: Are there specific regions within the city that have distinct patterns of time limits, and how do these patterns affect parking rates? Do areas with shorter time limits tend to have lower parking rates, and vice versa? I would like to explore the distribution and relationship of parking rates and time limits in different areas within the city.

**Variable of interest**: avg_rate

<!----------------------------------------------------------------------------->

## 3.1 (3 points)

Fit a model or run a hypothesis test that provides insight on this variable with respect to the research question. Store the model object as a variable, and print its output to screen. We'll omit having to justify your choice, because we don't expect you to know about model specifics in STAT 545.

-   **Note**: It's OK if you don't know how these models/tests work. Here are some examples of things you can do here, but the sky's the limit.

    -   You could fit a model that makes predictions on Y using another variable, by using the `lm()` function.
    -   You could test whether the mean of Y equals 0 using `t.test()`, or maybe the mean across two groups are different using `t.test()`, or maybe the mean across multiple groups are different using `anova()` (you may have to pivot your data for the latter two).
    -   You could use `lm()` to test for significance of regression coefficients.

<!-------------------------- Start your work below ---------------------------->

```{r}
ex3.1 <- lm(avg_rate ~ avg_time, m2.1)
ex3.1
```

<!----------------------------------------------------------------------------->

## 3.2 (3 points)

Produce something relevant from your fitted model: either predictions on Y, or a single value like a regression coefficient or a p-value.

-   Be sure to indicate in writing what you chose to produce.
-   Your code should either output a tibble (in which case you should indicate the column that contains the thing you're looking for), or the thing you're looking for itself.
-   Obtain your results using the `broom` package if possible. If your model is not compatible with the broom function you're needing, then you can obtain your results by some other means, but first indicate which broom function is not compatible.

<!-------------------------- Start your work below ---------------------------->

Regression coefficients:

```{r}
library(broom)
ex3.2 <- tidy(ex3.1)
ex3.2
```

Predictions:

```{r}
ex3.2.1 <- augment(ex3.1, newdata = tibble(avg_time = 1:24))
glimpse(ex3.2.1)
```

<!----------------------------------------------------------------------------->

# Task 4: Reading and writing data

Get set up for this exercise by making a folder called `output` in the top level of your project folder / repository. You'll be saving things there.

## 4.1 (3 points)

Take a summary table that you made from Task 1, and write it as a csv file in your `output` folder. Use the `here::here()` function.

-   **Robustness criteria**: You should be able to move your Mini Project repository / project folder to some other location on your computer, or move this very Rmd file to another location within your project repository / folder, and your code should still work.
-   **Reproducibility criteria**: You should be able to delete the csv file, and remake it simply by knitting this Rmd file.

<!-------------------------- Start your work below ---------------------------->

```{r}
# install.packages('here') 
path <- here::here("output","q2_opt3.2.csv")
dir.create('output')
write.csv(q2_opt3.2, file = path)
path
```

<!----------------------------------------------------------------------------->

## 4.2 (3 points)

Write your model object from Task 3 to an R binary file (an RDS), and load it again. Be sure to save the binary file in your `output` folder. Use the functions `saveRDS()` and `readRDS()`.

-   The same robustness and reproducibility criteria as in 4.1 apply here.

<!-------------------------- Start your work below ---------------------------->

```{r}
saveRDS(ex3.1,file= here::here("output","model.rds"))
model <- readRDS(here::here("output","model.rds"))
model
```

<!----------------------------------------------------------------------------->

# Overall Reproducibility/Cleanliness/Coherence Checklist

Here are the criteria we're looking for.

## Coherence (0.5 points)

The document should read sensibly from top to bottom, with no major continuity errors.

The README file should still satisfy the criteria from the last milestone, i.e. it has been updated to match the changes to the repository made in this milestone.

## File and folder structure (1 points)

You should have at least three folders in the top level of your repository: one for each milestone, and one output folder. If there are any other folders, these are explained in the main README.

Each milestone document is contained in its respective folder, and nowhere else.

Every level-1 folder (that is, the ones stored in the top level, like "Milestone1" and "output") has a `README` file, explaining in a sentence or two what is in the folder, in plain language (it's enough to say something like "This folder contains the source for Milestone 1").

## Output (1 point)

All output is recent and relevant:

-   All Rmd files have been `knit`ted to their output md files.
-   All knitted md files are viewable without errors on Github. Examples of errors: Missing plots, "Sorry about that, but we can't show files that are this big right now" messages, error messages from broken R code
-   All of these output files are up-to-date -- that is, they haven't fallen behind after the source (Rmd) files have been updated.
-   There should be no relic output files. For example, if you were knitting an Rmd to html, but then changed the output to be only a markdown file, then the html file is a relic and should be deleted.

Our recommendation: delete all output files, and re-knit each milestone's Rmd file, so that everything is up to date and relevant.

## Tagged release (0.5 point)

You've tagged a release for Milestone 2.

### Attribution

Thanks to Victor Yuan for mostly putting this together.
